Operator evolution from the similarity renormalization group and the Magnus expansion

### 2019-11-18 Notes/Operator_evolution/operator_evolution.tex
Minor updates to operator evolution draft

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
\subsection{The Magnus expansion}
\label{sec:magnus_expansion}

@@

\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
	%\caption{Caption.}
	\label{fig:potential_slices_high_cutoffs_Wegner}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
	%\caption{Caption.}
	\label{fig:potential_slices_high_cutoffs_T}
\end{figure}
\begin{table}
	\captionsetup{singlelinecheck=false,justification=raggedright}
	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus-evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
	\label{tab:energies}
	\begin{ruledtabular}
		\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
      			$  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
			\colrule
      			SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
      			Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
      			Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
      			SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
      			Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
      			Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
		\end{tabular}
  	\end{ruledtabular}
\end{table}

>>>>

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
\subsection{The Magnus expansion: Formalism}
\label{sec:magnus_expansion_formalism}

@@

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
\subsection{The Magnus expansion: Results}
\label{sec:magnus_expansion_results}

%
\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
	\caption{Caption.}
	\label{fig:potential_slices_high_cutoffs_Wegner}
\end{figure}
%
\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
	\caption{Caption.}
	\label{fig:potential_slices_high_cutoffs_T}
\end{figure}
%
%
\begin{table}
	\captionsetup{singlelinecheck=false,justification=raggedright}
	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus-evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
	\label{tab:energies}
	\begin{ruledtabular}
		\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
      			$  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
			\colrule
      			SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
      			Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
      			Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
      			SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
      			Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
      			Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
		\end{tabular}
  	\end{ruledtabular}
\end{table}
